Fit by design: Developing substrate-specific seed mixtures for functional dike restoration

### 2023-02-23 manuscript.Rmd
Update manuscript.Rmd

1.  Sowing is a well-established restoration technique to overcome dispersal limitation and site-specific seed mixtures are most effective to achieve functional communities. This is especially important if the restored vegetation has to protect critical infrastructure like roadsides and dikes. Here, an improved seed--substrate combination would secure slope stability, reduce mowing efforts, and generate biodiverse grasslands.
2.  A factorial field experiment addressed this topic on a dike at river Danube in S Germany in the period 2018--2021. On 288 plots, we tested three sand admixtures, two substrate depths, two seed densities and two seed mixtures (mesic hay meadow, calcareous grassland) in north or south exposition, and measured the persistence of sown species, the Favorable Conservation Status (FCS), and the successional distance to reference sites as calculated from an ordination.
3.  Sand admixture had a slightly positive effect on target variables, while substrate depth, seed density and mixture type had no effects on species persistence or FCS.
4.  Overall, the sown vegetation developed in the desired direction, but a recovery debt remained after four years, and some plots still showed similarities to negative references from ruderal sites. In north exposition, hay meadow-seed mixtures developed closer to the respective reference communities than dry grasslands.
5.  In south exposition, the sown communities developed poorly which might be due to a severe drought during establishment and the addition and removal of a geotextile. This initial negative effect remained over the entire observation period.
6.  Synthesis and applications: Site-adapted seed mixtures make restoration more efficient. However, applying several seed--substrate combinations might foster beta diversity. Furthermore, additional efforts in management might be necessary to reduce the recovery debt and re-sowing after unfavorable conditions is recommended.

@@

Favorable Conservation Status

@@

Grasslands can support a very high biodiversity and they provide several ecosystem services [@Dengler.2014; @Bardgett.2021]. However, they are globally endangered [@Bardgett.2021] for example by misguided afforestation [@dudley2020], and in Europe, calcareous grasslands and hay meadows are red-listed habitats [Category 3, 'vulnerable', @Janssen.2016]. Restoration is seen as a key factor to sustain biodiversity and ecosystem services [@COP.2014; @UnitedNations.2019b], and sowing is a well-established approach to establish species-rich grasslands [@Kiehl.2010]. Sowing high-diversity mixtures of local provenance produced by specialized companies is a promising way to scale up restoration efforts [@Freitag.2021], and to overcome the dispersal filters [@myers2009; @orrock2023]. However, there are still open questions about adjusting the seed mixtures to specific site conditions and future climate conditions [@Torok.2021].

@@

To measure the success of restoration, we chose four indices. First, we observed the persistence of the sown species, which is a key objective of this restoration measure [@Wilsey.2021]. For this purpose, presence of the sown species was monitored for three consecutive years. Second, we calculated the Favorable Conservation Status (FCS) which distinguishes characteristic diversity and derived diversity [@Helm.2015]. Characteristic diversity is created by established species which belong to the habitat-specific species pool. In other words, these species are associated with the habitat type of interest. Third, the successional distance to the reference grasslands was determined. This measure quantifies the ordination distance of a plot to the average reference site [@Rydgren.2019]. To complement these indices, the success of restoration or the difference from desired conditions was evaluated [cf. @Brudvig.2017b]. This was reached by comparing the species composition of the experimental plots with reference sites. We asked the following question to evaluate the restoration approaches and the success after four years:

@@

2.  How strong differs the Favorable Conservation Status (FCS) among the seed--substrate combinations?

@@

The target vegetation were lowland mesic hay meadows and semi-dry calcareous grassland [EUNIS code: R22, R1A, @Chytry.2020, 'Arrhenatherion elatioris' and 'Cirsio-Brachypodion pinnati' according to the EuroVegChecklist: CM01A, DA01B, @mucina2016]. The species pool of hay meadows and dry grasslands consisted of 55 and 58 species, respectively. The seeds were received from a commercial producer of autochthonous seeds (Co. Krimmer, Pulling). From these species pools, 20 species were randomly selected for each plot (Appendix A2). The seed mixtures always contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(tab:seedmix)). The community-weighted means (CWM) of functional traits differed between the seed mixture types (Appendix A3). As expected, the hay-meadow mixtures had a higher specific leaf area (SLA), lower seed mass, and higher canopy height than the dry-grassland mixtures. The south-exposed plots were sown in mid-April 2018 and the north exposition 14 days later. Due to the drought, the south exposition was protected by a geotextile consisting of straw chaff (350 g m^-2^) which was removed after two weeks due to unsatisfactory effects like the death of several protected lizards. The management started with a cut without hay removal and a mowing height of 20 cm in August 2018, followed by standard deep cuts with hay removal in July 2019 and 2020. In October 2018, *Bromus hordeaceus* was sown as a nursery grass to provide safe sites under drought conditions.

@@

Under the substrate, a 5 cm thick drainage layer of gravel (0-16 mm) was installed. Soil samples of the three substrates were tested on both expositions by mixing several sub-samples from different plots. The sand admixture changed the soil texture, increased the C/N ratio, reduced Calciumcarbonat, but did hardly change the pH values which were in the weak alkaline range (Table \@ref(tab:substrate)). The pH values correspond to a well established dike vegetation on river Rhine [@husicka2003], phosphate and potassium were rather scarce for agricultural soils and magnesium high [@lfl2022]. The vegetation was surveyed in June or July 2018--2021 [@BraunBlanquet.1964] and Londo scale was used [@londo1976]. The establishment rates of species are recorded in Appendix A4. In total, 48 species of the species pool of hay meadows (87%) and 46 (79%) of dry grasslands established by 2021, which are rather good ratios [@hedberg2010]. The species established 31 ± 22% of their sown plot. In total, 274 species were detected (Appendix A5).

@@

The ordination presents the experimental plots also in context with reference sites (Figure \@ref(fig:nmds)). The reference sites had a larger variation than the seed mixtures and were close to the seed mixtures but hardly overlapped. The positions of reference sites were shifted to the left in comparison to the seed mixtures, which means in the direction of early successional states. Though, they were still different from the negative references of ruderal vegetation. Negative references were only available on the south exposition and they were located in the NMDS between the positive reference sites and the state of restored plots in 2021. Hay meadow-seed mixtures led to a closer development to hay meadow references than dry grasslands to their references (Figure \@ref(fig:effects), \@ref(fig:recovery)) this was especially the case on the north exposition (Figure \@ref(fig:nmds)).

@@

Restoration on agricultural soils can have limited success due to high nutrient loads [@walker2004] but mixing with a mineral compnent need not necessarily improve the outcome [@chenot-lescure2022]. Similarly to that study in France, sand admixture reduced nutrient loads and led to higher persistence of sown species while 50% admixture did not further increase the effect. In addition, the effect only appeared in north exposition and the effect size of about 6% in the fourth year after restoration was rather small. The Favorable Conservation Status (FCS) was hardly affected by sand admixture which corresponds to the experiment in a quarry [@chenot-lescure2022]. Substrate depth did not significantly affect persistence or FCS similarly to earlier studies [@baer2004]. Larger differences in soil depths might be necessary to observe negative effects by thicker substrate layers as was shown for prairies [@dornbush2010]. Neither, seed density had an effect on persistence and FCS which fits to results of @Kaulfuss.2022, who found out that a certain amount of seeds are necessary for a successful establishment of target species but higher densities do not further improve the result and have rather a slight negative effect.

The vegetation in south exposition had a different species composition which confirms the findings of @Batori.2016 in Hungary. Here, the differences might have some unwanted experimental reasons: the geotextile, which had been implemented on the southern slope, was removed after two weeks. This led to the drying of many seedlings which was amplified by the intense drought of 2018 and 2019 [@hari2020]. This drought could have decreased germination and establishment of sown species also in general because a moist spring with a mesic temperature improves establishment [@Larson.2021; @orrock2023]. The interesting point here is the lasting negative effect on persistence and FCS which suggests a legacy effect by adverse weather conditions after sowing as it was observed by other studies [@Stuble.2017; @Groves.2020]. The problems during the establishment phase might have led to an alternative trajectory [@suding2004] and could probably only be met by re-sowing. The drying of seedlings might also have leveled the distinction of the seed mixture types on the south exposition.

@@

Our aim was to identify the best seed--substrate combination in respect of restoration effectiveness and biodiversity. For evaluating effectiveness, we measured the persistence of the sown species and for fostering plant biodiversity in general, we measured the FCS. Though, we could not identify an interaction effect for neither of the indices. We would have expected a better performance of hay-meadow seed mixtures with lower sand admixture and for dry grasslands with higher sand admixture. Our results suggest that, at least after four years, the substrate conditions are within the range of both seed mixture types (hay meadows, dry grasslands). Although, both types are clearly plant-sociologically and functionally distinct, they are still relative closely related why they contain shared species and could develop on similar site conditions with modified sub-associations[Appendix A3, @Oberdorfer.1993; @Oberdorfer.1993b; @husicka2003]. Other grassland studies could identify more or less clear interactions of opposing habitat preferences or functional traits along the gradients of productivity, moisture, and nutrients [@Zirbel.2020; @Freitag.2021; @Kaulfuss.2022]. However, these studies did not work with an experimental set up of different seed--substrate combinations, but analyzed the result of habitat and biotic filtering after one, five and about 15 years, respectively. Furthermore, the non-existence of an ideal combination could be explained by priority effects which means that the species of the non-perfect seed mixture could establish earlier and preempted the available niches for the species of related habitat types [@Fukami.2015].

@@

The seed mixtures and positive reference sites were similar but hardly overlapped (Figure \@ref(fig:nmds)). The position on the NMDS suggests that the seed mixture represent a later successional stage than the references. The NMDS shows a slightly better adaption of hay meadows to the north exposition than of dry grasslands (Figure \@ref(fig:recovery)). This can be expected from the requirements of hay meadows for mesic conditions which can be provided on north exposed dike slopes [@Batori.2020; @Oberdorfer.1993b]. On the southern exposition, the plots of hay meadows developed rather to dry grassland references which indicates an inefficient restoration by using an non-adapted seed mixture.

@@

```{r tab.id = "seedmix", ft.align = "left", tab.cap = "Each plot received an individual set of 20 species with some restrictions to the number of species per functional group. The total species pool for hay meadows was 55 and for dry grassland 58. In total, plots received 16 or 32 g of seeds. All individual seed mixtures are stored in Appendix A2."}
read_csv(here::here("data", "raw", "data_raw_table_1_seedmix.csv"),
         show_col_types = FALSE) %>%
  slice(-1) %>%
  flextable() %>%
  merge_at(part = "header", j = 2:3) %>%
  align(align = "center", part = "all", j = -1) %>%
  add_header_row(top = FALSE, values = c("", "Hay meadow", "Dry grassland", "", "", "")) %>%
  add_header_row(top = FALSE, values = c("", "#", "#", "#", "wt%", "wt%")) %>%
  bold(part = "header", i = 1) %>%
  border_inner_h(part = "header", border = fp_border(width = 1)) %>%
  autofit()
```

@@

```{r fig.id = "effects", fig.asp = 0.3030, fig.width = 6.49, fig.cap = "The posterior density distributions (grey) of the treatments calculated over all four surveyed years of sown grassland communities at a river dike. Furthermore, the median and the 66% and 95% credible intervals are shown: the persistence of sown species (A), the Favorable Conservation Status (FCS; B) and the successional distance to reference (recovery; C). The FCS is the ratio of target species and non-target species. Note that the zero lines indicate that both levels have equal values. This means for instance that hay meadows are closer to their reference than dry grasslands  (C)."}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm.tiff")
  )
```

@@

```{r fig.id = "persistence", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "Persistence of sown species of sown grassland communities at a river dike. The plots had substrates with different sand admixtures and were sown with two different seed mixture types. Per plot 20 species were sown. Shown are the medians and 95% credible intervals of the posterior distributions which were derived from a Bayesian linear mixed-effects model (BLMM)."}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x8cm.tiff")
  )
```

@@

```{r fig.id = "fcs", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The Favorable Conservation Status (FCS) of sown grassland communities at a river dike. The plots had substrates with different sand admixtures and were sown with two different seed mixtures. The zero line indicate that target and non-target species are balanced. Positive values indicate that there are more target species. Shown are the medians and 95% credible intervals of the posterior distributions which were derived from a Bayesian linear mixed-effects model (BLMM)."}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x8cm.tiff")
  )
```

>>>>

1.  Sowing is a well-established restoration technique to overcome dispersal limitation and site-specific seed mixtures are most effective to achieve functional communities. This is especially important if the restored vegetation has to protect critical infrastructure like roadsides and dikes. Here, an improved seed--substrate combination would secure slope stability, reduce mowing efforts, and generate biodiverse grasslands.
2.  A factorial field experiment addressed this topic on a dike at river Danube in S Germany in the period 2018--2021. On 288 plots, we tested three sand admixtures, two substrate depths, two seed densities and two seed mixtures (mesic hay meadow, calcareous grassland) in north or south exposition, and measured the persistence of sown species, the Favourable Conservation Status (FCS), and the successional distance to reference sites as calculated from an ordination.
3.  Sand admixture had a slightly positive effect on target variables, while substrate depth, seed density and mixture type had no effects on species persistence or FCS.
4.  Overall, the sown vegetation developed in the desired direction, but a recovery debt remained after four years, and some plots still showed similarities to negative references from ruderal sites. In north exposition, hay meadow-seed mixtures developed closer to the respective reference communities than dry grasslands.
5.  In south exposition, the sown communities developed poorly which might be due to a severe drought during establishment and the addition and removal of a geotextile. This initial negative effect remained over the entire observation period.
6.  Synthesis and applications: Site-adapted seed mixtures make restoration more efficient. However, applying several seed--substrate combinations might foster beta diversity. Furthermore, additional efforts in management might be necessary to reduce the recovery debt and re-sowing after unfavourable conditions is recommended.

@@

Favourable Conservation Status

@@

Grasslands can support a exceedingly high biodiversity and they provide several ecosystem services [@Dengler.2014; @Bardgett.2021]. However, they are globally endangered [@Bardgett.2021] for example by misguided afforestation [@dudley2020], and in Europe, calcareous grasslands and hay meadows are red-listed habitats [Category 3, 'vulnerable', @Janssen.2016]. Restoration is seen as a key factor to sustain biodiversity and ecosystem services [@COP.2014; @UnitedNations.2019b], and sowing is a well-established approach to establish species-rich grasslands [@Kiehl.2010]. Sowing high-diversity mixtures of local provenance produced by specialized companies is a promising way to scale up restoration efforts [@Freitag.2021], and to overcome the dispersal filters [@myers2009; @orrock2023]. However, there are still open questions about adjusting the seed mixtures to specific site conditions and future climate conditions [@Torok.2021].

@@

To measure the success of restoration, we chose four indices. First, we observed the persistence of the sown species, which is a key objective of this restoration measure [@Wilsey.2021]. For this purpose, presence of the sown species was monitored for three consecutive years. Second, we calculated the Favourable Conservation Status (FCS) which distinguishes characteristic diversity and derived diversity [@Helm.2015]. Characteristic diversity is created by established species which belong to the habitat-specific species pool. In other words, these species are associated with the habitat type of interest. Third, the successional distance to the reference grasslands was determined. This measure quantifies the ordination distance of a plot to the average reference site [@Rydgren.2019]. To complement these indices, the success of restoration or the difference from desired conditions was evaluated [cf. @Brudvig.2017b]. This was reached by comparing the species composition of the experimental plots with reference sites. We asked the following question to evaluate the restoration approaches and the success after four years:

@@

2.  How strong differs the Favourable Conservation Status (FCS) among the seed--substrate combinations?

@@

The target vegetation was lowland mesic hay meadows and semi-dry calcareous grassland [EUNIS code: R22, R1A, @Chytry.2020, 'Arrhenatherion elatioris' and 'Cirsio-Brachypodion pinnati' according to the EuroVegChecklist: CM01A, DA01B, @mucina2016]. The species pool of hay meadows and dry grasslands consisted of 55 and 58 species, respectively. The seeds were received from a commercial producer of autochthonous seeds (Co. Krimmer, Pulling). From these species pools, 20 species were randomly selected for each plot (Appendix A2). The seed mixtures always contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(tab:seedmix)). The community-weighted means (CWM) of functional traits differed between the seed mixture types (Appendix A3). As expected, the hay-meadow mixtures had a higher specific leaf area (SLA), lower seed mass, and higher canopy height than the dry-grassland mixtures. The south-exposed plots were sown in mid-April 2018 and the north exposition 14 days later. Due to the drought, the south exposition was protected by a geotextile consisting of straw chaff (350 g m^-2^) which was removed after two weeks due to unsatisfactory effects like the death of several protected lizards. The management started with a cut without hay removal and a mowing height of 20 cm in August 2018, followed by standard deep cuts with hay removal in July 2019 and 2020. In October 2018, *Bromus hordeaceus* was sown as a nursery grass to provide safe sites under drought conditions.

@@

Under the substrate, a 5 cm thick drainage layer of gravel (0-16 mm) was installed. Soil samples of the three substrates were tested on both expositions by mixing several sub-samples from different plots. The sand admixture changed the soil texture, increased the C/N ratio, reduced Calciumcarbonat, but did hardly change the pH values which were in the weak alkaline range (Table \@ref(tab:substrate)). The pH values correspond to a well-established dike vegetation on river Rhine [@husicka2003], phosphate and potassium were rather scarce for agricultural soils and magnesium high [@lfl2022]. The vegetation was surveyed in June or July 2018--2021 [@BraunBlanquet.1964] and Londo scale was used [@londo1976]. The establishment rates of species are recorded in Appendix A4. In total, 48 species of the species pool of hay meadows (87%) and 46 (79%) of dry grasslands established by 2021, which are rather good ratios [@hedberg2010]. The species established 31 ± 22% of their sown plot. In total, 274 species were detected (Appendix A5).

@@

The ordination presents the experimental plots also in context with reference sites (Figure \@ref(fig:nmds)). The reference sites had a larger variation than the seed mixtures and were close to the seed mixtures but hardly overlapped. The positions of reference sites were shifted to the left in comparison to the seed mixtures, which means in the direction of early successional states. Though, they were still different from the negative references of ruderal vegetation. Negative references were only available on the south exposition and they were located in the NMDS between the positive reference sites and the state of restored plots in 2021. Hay meadow-seed mixtures led to a closer development to hay meadow references than dry grasslands to their references (Figure \@ref(fig:effects), \@ref(fig:recovery)) this was especially the case on the north exposition (Figure \@ref(fig:nmds)). \clearpage \newpage

@@

Restoration on agricultural soils can have limited success due to high nutrient loads [@walker2004] but mixing with a mineral component need not necessarily improve the outcome [@chenot-lescure2022]. Similarly to that study in France, sand admixture reduced nutrient loads and led to higher persistence of sown species while 50% admixture did not further increase the effect. In addition, the effect only appeared in north exposition and the effect size of about 6% in the fourth year after restoration was rather small. The Favourable Conservation Status (FCS) was hardly affected by sand admixture which corresponds to the experiment in a quarry [@chenot-lescure2022]. Substrate depth did not significantly affect persistence or FCS similarly to earlier studies [@baer2004]. Larger differences in soil depths might be necessary to observe negative effects by thicker substrate layers as was shown for prairies [@dornbush2010]. Neither, seed density had an effect on persistence and FCS which fits to results of @Kaulfuss.2022, who found out that a certain amount of seeds are necessary for a successful establishment of target species but higher densities do not further improve the result and have rather a slight negative effect.

The vegetation in south exposition had a different species composition which confirms the findings of @Batori.2016 in Hungary. Here, the differences might have some unwanted experimental reasons: the geotextile, which had been implemented on the southern slope, was removed after two weeks. This led to the drying of many seedlings which was amplified by the intense drought of 2018 and 2019 [@hari2020]. This drought could have decreased germination and establishment of sown species also in general because a moist spring with a mesic temperature improves establishment [@Larson.2021; @orrock2023]. The interesting point here is the lasting negative effect on persistence and FCS which suggests a legacy effect by adverse weather conditions after sowing as it was observed by other studies [@Stuble.2017; @Groves.2020]. The problems during the establishment phase might have led to an alternative trajectory [@suding2004] and could probably only be met by re-sowing. The drying of seedlings might also have levelled the distinction of the seed mixture types on the south exposition.

@@

Our aim was to identify the best seed--substrate combination in respect of restoration effectiveness and biodiversity. For evaluating effectiveness, we measured the persistence of the sown species and for fostering plant biodiversity in general, we measured the FCS. Though, we could not identify an interaction effect for neither of the indices. We would have expected a better performance of hay-meadow seed mixtures with lower sand admixture and for dry grasslands with higher sand admixture. Our results suggest that, at least after four years, the substrate conditions are within the range of both seed mixture types (hay meadows, dry grasslands). Although, both types are clearly plant-sociologically and functionally distinct, they are still relative closely related why they contain shared species and could develop on similar site conditions with modified sub-associations [Appendix A3, @husicka2003; @Oberdorfer.1993]. Other grassland studies could identify more or less clear interactions of opposing habitat preferences or functional traits along the gradients of productivity, moisture, and nutrients [@Zirbel.2020; @Freitag.2021; @Kaulfuss.2022]. However, these studies did not work with an experimental set up of different seed--substrate combinations, but analysed the result of habitat and biotic filtering after one, five and about 15 years, respectively. Furthermore, the non-existence of an ideal combination could be explained by priority effects which means that the species of the non-perfect seed mixture could establish earlier and pre-empted the available niches for the species of related habitat types [@Fukami.2015].

@@

The seed mixtures and positive reference sites were similar but hardly overlapped (Figure \@ref(fig:nmds)). The position on the NMDS suggests that the seed mixture represent a later successional stage than the references. The NMDS shows a slightly better adaption of hay meadows to the north exposition than of dry grasslands (Figure \@ref(fig:recovery)). This can be expected from the requirements of hay meadows for mesic conditions which can be provided on north exposed dike slopes [@Batori.2020; @Oberdorfer.1993]. On the southern exposition, the plots of hay meadows developed rather to dry grassland references which indicates an inefficient restoration by using an non-adapted seed mixture.

@@

```{r tab.id = "seedmix", ft.align = "left", tab.cap = "Each plot received an individual set of twenty species with some restrictions to the number of species per functional group. The total species pool for hay meadows was 55 and for dry grassland 58. In total, plots received 16 or 32 g of seeds. All individual seed mixtures are stored in Appendix A2."}
read_csv(here::here("data", "raw", "data_raw_table_1_seedmix.csv"),
         show_col_types = FALSE) %>%
  slice(-1) %>%
  flextable() %>%
  merge_at(part = "header", j = 2:3) %>%
  align(align = "center", part = "all", j = -1) %>%
  add_header_row(top = FALSE, values = c("", "Hay meadow", "Dry grassland", "", "", "")) %>%
  add_header_row(top = FALSE, values = c("", "#", "#", "#", "wt%", "wt%")) %>%
  bold(part = "header", i = 1) %>%
  border_inner_h(part = "header", border = fp_border(width = 1)) %>%
  autofit()
```

@@

```{r fig.id = "effects", fig.asp = 0.3030, fig.width = 6.49, fig.cap = "The posterior density distributions (grey) of the treatments calculated over all four surveyed years of sown grassland communities at a river dike. Furthermore, the median and the 66% and 95% credible intervals are shown: the persistence of sown species (A), the Favourable Conservation Status (FCS; B) and the successional distance to reference (recovery; C). The FCS is the ratio of target species and non-target species. Note that the zero lines indicate that both levels have equal values. This means for instance that hay meadows are closer to their reference than dry grasslands  (C)."}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm.tiff")
  )
```

@@

```{r fig.id = "persistence", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "Persistence of sown species of sown grassland communities at a river dike. The plots had substrates with different sand admixtures and were sown with two different seed mixture types. Per plot twenty species were sown. Shown are the medians and 95% credible intervals of the posterior distributions which were derived from a Bayesian linear mixed-effects model (BLMM)."}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x8cm.tiff")
  )
```

@@

```{r fig.id = "fcs", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The Favourable Conservation Status (FCS) of sown grassland communities at a river dike. The plots had substrates with different sand admixtures and were sown with two different seed mixtures. The zero line indicate that target and non-target species are balanced. Positive values indicate that there are more target species. Shown are the medians and 95% credible intervals of the posterior distributions which were derived from a Bayesian linear mixed-effects model (BLMM)."}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x8cm.tiff")
  )
```
